\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Egor Verkhozin} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+7 (914) 000-9112 \\ Saint-Petersburg} 
\address{\href{mailto:ea@verkhozin.ru}{ea@verkhozin.ru} \\ \href{https://linkedin.com/company/faangpath}{Portfolio}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf System and Applied Software}, ITMO \hfill {2024 - Present}\\


{\bf Applied Data Analysis and Artificial Intelligence}, Highest School of Economics (HSE) \hfill {2023 - 2024}\\

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript, Python, Swift, SQL (PostgreSQL, SQLite, Redis) \\
Frameworks & Next.js, React.js, Node.js, FastAPI, Flask, SwiftUI, Angular, Vue.js \\ 
Developer Tools & Git, Docker, VS Code, Xcode, Slack\\
Soft Skills & Leadership, Strong Work Ethic, Communication, UI/UX Awareness\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Team Lead} \hfill Dec 2024 - Aug 2025 \\
OrbosAI \hfill \textit{Moscow}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Introduced AI workflows to the team, which led to 440\% growth in productivity
    %  \item Achieved X\% growth for XYZ using A, B, and C skills.
    %  \item Led XYZ which led to X\% of improvement in ABC
    % \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}
 

\textbf{Full-Stack Developer} \hfill Nov 2023 - Dec 2024\\
Hunt.ME \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item 
    %  \item Led XYZ which led to X\% of improvement in ABC
    % \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}

 \textbf{Full-Stack Developer} \hfill 2020 - 2023\\
Freelance \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Completed 30+ small to medium-sized projects at Fiverr and Upwork
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
    \item	Sample bullet point.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
\end{itemize}


\end{rSection}


\end{document}
